Bullet Groups as a test of $\Lambda$CDM

### 2014-03-06 paper/ms.tex
descoping to have a letter

\section{Simulation and halo catalogs}
\label{sec:simulation}

@@

The ranges of circular velocities for the host and sub-halos and the
corresponding number of halos at every redshift are listed in Table
\ref{table1}.

\begin{table*}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample  & Minimum $V_{\rm c}$ & Maximum $V_{\rm c}$  & \# Halos & \#
Halos  & \# Halos & \# Halos \\ 
 & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host   & 300 & XX &    400    &   362     &   310    &  192   \\ 
Sub-structure & 75  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
\end{tabular} 
\caption{Circular velocity ranges for the halos and subhalos at
  different redshifts.}  
\label{table1}
\end{center}
\end{table*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{New_figures/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and
  sub-structure (black circle) in the sample.}  
\label{fig:configuration}
\end{figure}

The configuration of the BGs in the simulations is shown in Figure
\ref{fig:configuration}. There we depict a host and its most massive
sub-halo from in a particular case found at z$=0$. The arrows show the
position and the velocity vectors sub-halo in a frame of reference
where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
vectors characterized by, 
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} 
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_4_300kms_700kms.eps}
\end{center}
\caption{x}
\label{fig:velocities}
\end{figure*}

@@

\section{Discussion}
\label{sec:discussion}

>>>>

\section{Simulation, halo catalogs and pairs}
\label{sec:simulation}

@@

We use halo catalogs constructed using the BDM algorithm. [...]

In the snapshots at redshift $z=0.0,0.25, 0.5$ and $1.0$ there are
$XX, XX, XX, XX$ host halos with circular velocities $V_{\rm c}>
300$\kms and $XX, XX, XX, XX$ sub-halos with circular velocities
$V_{\rm c}>75$\kms. These two sets of halos constitute the basis for
our analysis.

For each host halo in the sample we find its most massive
sub-halo. Each pair host/sub-halo is considererd as a potential Bullet
Group and is kept for the measurement and analysis described in the
next section.

@@

The Bullet groups is composed by two halos. the host halo and the sub
halo. This configuration is described by the position and velocity of
the sub-halo in a frame of reference where the main halo is at rest;
thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and 
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, where the subscripts $host$
and $sub$ refer to the host and sub-halo in the frame of reference of
the simulation, respectively.

The angle between these two vectors characterized by, 
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} 
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

@@

Figure \ref{fig:} presents the geometry of the bullet groups in our 
 the relative geometry of the collision using the
variables $\mu$ and $X_{\rm off}$.

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_4_300kms_700kms.eps}
\end{center}
\caption{x}
\label{fig:geometry}
\end{figure*}

@@
